\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}



\begin{document}
\name{\LARGE{Nilay Sadavarte}}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: (413) 461-6925       \hfill LinkedIn: \url{www.linkedin.com/in/nsadavarte} 
    \\
    \noindent Email: nilay18sadavarte@gmail.com  \hfill GitHub: \url{www.github.com/nilay1808}
    \\
    \vspace{-4.5mm}

    % Education
    \section{\mysidestyle Education}

    \textbf{University of Massachusetts, Amherst} \hfill Amherst, MA
    \\
    \textsl{Bachelor of Science in Computer Science; Minor: Mathematics} \hfill \textsl{Aug 2017 -- Dec 2020} 
    \\
    • GPA 3.5; Dean’s List; Commonwealth Honors College;
    \\
    • Chancellor’s Scholarship; Outstanding Leadership Award (2018, 2019)
    % \\
    % • Relevant Coursework:
    % \\
    % \hphantom{5mm} \textit{Software Engineering \& Design, Database Systems, Algorithms, Systems Programming, Discrete Math \& Computation, Math Modeling, Functional Programming, Statistics, Calculus, Data Structures}

    % EXPERIENCE
    \section{\mysidestyle Professional\\Experience}

    % FB
    \textbf{Facebook} \hfill Menlo Park, CA
    \\
    \textsl{Software Engineering Intern} \hfill \textsl{May 2020 -- Aug 2020}
    \\
    •   Incoming summer 2020.
    % 
    \\ \vspace{-1.5mm} \\
    % 
    % LRC
    \textbf{University of Massachusetts, Amherst} \hfill Amherst, MA
    \\
    \textsl{Tech Lead} \hfill \textsl{Sept 2019 -- Present}
    \\
    •	Working as the lead developer to maintain, debug and refactor legacy code for the proprietary Tutoring Scheduling Platform for a staff of over 400 which is used by over 4000 students per week.
    \\
    •	Redesigned the website to be more responsive on mobile devices and perform better with slower internet connections and removed redundancies from the SQL database and tuned it for 30\% faster query speeds.
    % 
    \\ \vspace{-1.5mm} \\
    % 
    % Uber
    \textbf{Uber} \hfill San Francisco, CA
    \\
    \textsl{Software Engineering Fellow} \hfill \textsl{April 2019 -- Dec 2019}
    \\
    •	Part of Uber’s Career Prep (Hidden Genius) Program, accepted as one of 30 fellows selected from a pool of over 800 applicants based on leadership potential, technical skills, and personal achievement.
    \\
    •	Attended regular workshops taught by Uber engineers at various offices and worked on projects with the backend, ATG, and payments teams.
    % 
    \\ \vspace{-1.5mm} \\
    % 
    % RA
    \textbf{University of Massachusetts, Amherst} \hfill Amherst, MA
    \\
    \textsl{Resident Assistant} \hfill \textsl{Aug 2018 -- Present}
    \\
    •	Managed a floor of 95 first-year students and helped them with their transition to college.
    \\
    •	Worked on community development, student learning initiatives, and incident response. 
    \\
    •	Designed awareness posters and acted as a social and academic role-model. Facilitated floor meetings and roommate conflicts.
    % % 
    % \\ \vspace{-1.5mm} \\
    % % 
    % % Greeno
    % \textbf{Greeno Sub Shop} \hfill Amherst, MA
    % \\
    % \textsl{Co-Manager} \hfill \textsl{Sept 2017 -- Aug 2019}
    % \\
    % •	Wrote Python scripts to automate and monitor payroll processes and sales.
    % \\
    % •	Redesigned the website to be user-friendly, used analytics to track user flow and improve design.
    % \\
    % •	Worked on the logistics team and coordinated dates and schedules along with security access.
    
    
    % ACTIVITIES
    \section{\mysidestyle Activities}

    % BUILD
    \textbf{BUILD UMass} \hfill Amherst, MA
    \\
    \textsl{Co-founder \& President} \hfill \textsl{Sept 2018 -- Present}
    \\
    •	Started the organization with a focus on software engineering and web development for non-profits and small businesses and grew it to over 40 members in 3 semesters.
    \\
    •	Currently supporting 5 teams with product management, execution strategies, and code reviews.
    \\
    •	Led technical workshops for over 200 students at various hackathons and organized several events.
    % 
    \\ \vspace{-1.5mm} \\
    % 
    % CSB
    \textbf{UMass Center for Student Business} \hfill Amherst, MA
    \\
    \textsl{Co-Manager} \hfill \textsl{Sept 2017 -- Aug 2019}
    \\
    •	Wrote Python scripts to automate and monitor payroll processes and sales.
    \\
    •	Redesigned the website to be user-friendly, used analytics to track user flow and improve design.
    \\
    •	Worked on the logistics team and coordinated dates and schedules along with security access.

    % PROJECTS
    \section{\mysidestyle Projects}

    \textbf{Survey Master} \hfill \textsl{Dec 2019}
    \\
    Worked in a scrum team of 8 to build an end-to-end survey platform where people can create, take, and analyze surveys. Used React.js for the frontend and Python (Flask) for the backend API.
    % 
    \\ \vspace{-1.5mm} \\
    % 
    \textbf{HR Bot} \hfill \textsl{Mar 2019}
    \\
    Designed a slackbot using Node.js to keep track of brownie points a member may receive each week. Uses basic NLP techniques to parse user messages and keeps track of points each member receives.

    % SKILLS
    \section{\mysidestyle Skills}

    \textbf{Programming:} Java, Python, JavaScript, C, Node.js, React.js, SQL, PHP, HTML, CSS, \LaTeX 
    \\
    \textbf{Development:} Git, Latex, FileZilla, Google Cloud, MongoDB, Heroku, Agile, Scrum
    \\
    \textbf{Languages:} English, Hindi, Marathi, German
\end{resume}
\end{document}
